---
  title: "This script computes the logistic regression models on frequency effects"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  theme: default
toc: yes
pdf_document:
  highlight: zenburn
toc: yes
editor_options: 
  chunk_output_type: console
---

```{r}
library(lme4)
library(ggplot2)
library(sjPlot)
library(emmeans)
library(ggthemes)
COLS=colorblind_pal()(8)
COLS = COLS[c(1,5,7)]
# library(tidyverse)

l_10_90_df <- read.csv("data/l_dataframes/dataframes/10L_90NL/combine.csv")
l_50_50_df <- read.csv("data/l_dataframes/dataframes/50L_50NL/combine.csv")
l_90_10_df <- read.csv("data/l_dataframes/dataframes/90L_10NL/combine.csv")

nl_10_90_df <- read.csv("data/nl_dataframes/dataframes/10L_90NL/combine.csv")
nl_50_50_df <- read.csv("data/nl_dataframes/dataframes/50L_50NL/combine.csv")
nl_90_10_df <- read.csv("data/nl_dataframes/dataframes/90L_10NL/combine.csv")

l_df = rbind(l_10_90_df,l_50_50_df,l_90_10_df)

nl_df = rbind(nl_10_90_df,nl_50_50_df,nl_90_10_df)

# table(df$prediction_status)
#table(table(df$triples))
# df.correct <- subset(df, df$prediction_status == 1)
# summary(df.correct)

## TODO: nested model comparison. Check AIC and BIC. BIC lower the better. more than 2 is significant. M1 = BIC of (1|run) and 1|model against 1|run, 1|model.

## to avoid overfitting we used BIC and AIC. best model justified by the data.
##


str(l_df)
table(l_df$model)
table(l_df$condition)
table(l_df$prediction_status)
l_df$prediction_status_f = as.factor(as.character(l_df$prediction_status))
contrasts(l_df$prediction_status_f)
levels(l_df$prediction_status_f)
l_df$frequency.log10 = log10(l_df$frequency)

l_df$condition_f_sc = factor(as.character(l_df$condition),
                levels = c("90L_10NL", "50L_50NL", "10L_90NL"))
contrasts(l_df$condition_f_sc) <- contr.sum(3)/2
contrasts(l_df$condition_f_sc)
colnames(contrasts(l_df$condition_f_sc)) <- c("90L_10NL_vs_grand", "50L_50NL_vs_grand")


l_model = glmer(prediction_status_f ~ frequency.log10 + condition_f_sc + frequency.log10:condition_f_sc + (1|triples) + (1|model), data=l_df, family="binomial")
summary(l_model)


ggplot_l_model = plot_model(l_model, type = "pred", terms = c("frequency.log10 [all]", "condition"), title = "")

ggplot_l_model = ggplot_l_model + xlab("Input frequency of stem consonants (log10)") + ylab("Predicted accuracy (in %)") + scale_color_discrete(labels = c("10%L-90%NL", "50%L-50%NL","90%L-10%NL"))+ theme(legend.position="bottom")
# + theme(legend.position = c(0.5, 1.1), legend.direction = "horizontal")
ggplot_l_model

cairo_pdf(filename = 'img/l_model_frequency_condition.pdf',
          height = 5,width = 5)
print(ggplot_l_model)
dev.off()
# plot_model(l_model, type = "pred", terms = c("condition"))


# l_df_50L_50NL = subset(l_df,condition=='50L_50NL')
# L_50L_50NL_model = glmer(prediction_status_f ~ frequency.log10  + (1|triples) + (1|model), data=l_df_50L_50NL, family="binomial")
# summary(L_50L_50NL_model)
# plot_model(L_50L_50NL_model, type = "pred", terms = c("frequency.log10 [all]"))
```


NL_shape itemns

```{r}
str(nl_df)
table(nl_df$model)
table(nl_df$condition)
table(nl_df$prediction_status)
nl_df$prediction_status_f = as.factor(as.character(nl_df$prediction_status))
contrasts(nl_df$prediction_status_f)
levels(nl_df$prediction_status_f)
nl_df$frequency.log10 = log10(nl_df$frequency)


nl_model = glmer(prediction_status_f ~ frequency.log10 + condition + frequency.log10:condition + (1|triples) + (1|model), data=nl_df, family="binomial")
summary(nl_model)

plot_model(nl_model, type = "pred", terms = c("frequency.log10 [all]", "condition"))
plot_model(nl_model, type = "pred", terms = c("condition"))

```


# save(reg_model, file="../../../data/fixed_run/analysis/memorization_generalization/l_shape/r_models/10L_90NL/glmer.rda")

# model = glmer(df.correct$prediction_status ~ df.correct$frequency + (1|df.correct$seen), family="logit", control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
# summary(model)


# model = lm(df$prediction_status ~ df$frequency.log, family="binomial", control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
# summary(model)

```
